### 2023-09-10 writing/manuscript.Rmd
add .bib file

---
bibliography: themusiclab.bib
csl: nature.csl
header-includes:
- \usepackage[left]{lineno}
- \usepackage{ragged2e}
- \usepackage{caption}
- \usepackage{longtable}
- \usepackage[labelformat = empty]{caption}
- \usepackage{afterpage}
- \usepackage{fontenc}
- \usepackage{soul}
- \usepackage{xcolor}
- \usepackage[symbol]{footmisc}
- \usepackage{numprint}
- \usepackage{lineno}
- \npthousandsep{,}
- \definecolor{bleu}{HTML}{2200cc}
- \renewcommand{\thefootnote}{\fnsymbol{footnote}}
notes-after-punctuation: no
urlcolor: bleu
linkcolor: bleu
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
editor_options:
  markdown:
    wrap: sentence
---

@@

source("../analysis/data_prep_sexdiff.R")
source("../analysis/fas.R")
source("../analysis/maha_v8c.R")

>>>>

---
bibliography: citations.bib
csl: nature.csl
header-includes:
- \usepackage[left]{lineno}
- \usepackage{ragged2e}
- \usepackage{caption}
- \usepackage{longtable}
- \usepackage[labelformat = empty]{caption}
- \usepackage{afterpage}
- \usepackage{fontenc}
- \usepackage{soul}
- \usepackage{xcolor}
- \usepackage[symbol]{footmisc}
- \usepackage{numprint}
- \usepackage{lineno}
- \npthousandsep{,}
- \definecolor{bleu}{HTML}{2200cc}
- \renewcommand{\thefootnote}{\fnsymbol{footnote}}
notes-after-punctuation: no
urlcolor: bleu
linkcolor: bleu
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
editor_options:
  markdown:
    wrap: sentence
---

@@

#source("../analysis/data_prep_sexdiff.R")
source("../analysis/fas.R")
source("../analysis/maha_v8c.R")
